Practical Effects of Integrating Temperature with Strang Split Reactions

### 2021-03-26 strang/paper.tex
add a verb

Type Ia supernovae, classical novae, X-ray bursts, and general stellar
evolution reactive flows, where the nuclear energy release can drive
strong convective or explosive flows.  These stellar flows require solving the equations of
hydrodynamics coupled with a nuclear reaction network.  The equations
of hydrodynamics with reacting sources are:
\begin{align}
\frac{\partial \rho}{\partial t} + \nabla \cdot (\rho \Ub) &= 0 \\
\frac{\partial (\rho X_k)}{\partial t} + \nabla \cdot (\rho X_k \Ub) &= \rho \omegadot_k \\
\frac{\partial (\rho \Ub)}{\partial t} + \nabla \cdot (\rho \Ub \Ub) + \nabla p &= 0 \\
\frac{\partial (\rho E)}{\partial t} + \nabla \cdot \left [ (\rho E + p) \Ub \right ] &= \rho \Sdot
\end{align}
where $\rho$ is the density, $\Ub$ is the velocity vector, $X_k$ are the species mass fractions
with creation rates $\omegadot_k$, $p$ is the pressure, $E$ is the
specific total energy, and $\Sdot$ is the nuclear energy generation rate.

>>>>

Type Ia supernovae, classical novae, X-ray bursts, and general stellar
evolution involve reactive flows, where the nuclear energy release can drive
strong convective or explosive flows.  These stellar flows require solving the equations of
hydrodynamics coupled with a nuclear reaction network.  The equations
of hydrodynamics with reacting sources are:
\begin{align}
\frac{\partial \rho}{\partial t} + \nabla \cdot (\rho \Ub) &= 0 \\
\frac{\partial (\rho X_k)}{\partial t} + \nabla \cdot (\rho X_k \Ub) &= \rho \omegadot_k \\
\frac{\partial (\rho \Ub)}{\partial t} + \nabla \cdot (\rho \Ub \Ub) + \nabla p &= 0 \\
\frac{\partial (\rho E)}{\partial t} + \nabla \cdot \left [ (\rho E + p) \Ub \right ] &= \rho \Sdot
\end{align}
where $\rho$ is the density, $\Ub$ is the velocity vector, $X_k$ are the species mass fractions
with creation rates $\omegadot_k$, $p$ is the pressure, $E$ is the
specific total energy, and $\Sdot$ is the nuclear energy generation rate.
